---
categories:  
- ""    #the front matter should be like the one found in, e.g., blog2.md. It cannot be like the normal Rmd we used
- ""
date: "2021-09-30"
description: This is one of the very first tasks that my team tackled in R. We were trying to visualise the countries with the most servings by alcohol type (i.e. beer, wine, and spirits) and comment on our findings.
draft: false
image:

keywords: ""
slug: code # slug is the shorthand URL address... no spaces plz
title: Alcohol Servings Project
---
  

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```

```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(ggrepel)   #Load ggrepel for geom_text_repel() graph in the inflation problem
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest) # to scrape wikipedia page
library(scales) #show returns as percentages
```



# Task 1: Where Do People Drink The Most Beer, Wine And Spirits?

Back in 2014, [fivethiryeight.com](https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/) published an article on alcohol consumption in different countries. We want to use the data in this article to find out in which countries people drink the most by looking at the consumption of **beer**, **wine**, and **spirits**.


```{r, load_alcohol_data}
library(fivethirtyeight)
data(drinks)

# or download directly
alcohol_direct <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv")

```


Let's take a look at our data and find whether there are any missing values and what variables we have. 

```{r glimpse_skim_data}
skim(alcohol_direct)
```
The dataset contains one character (qualitative) variable, namely `country`, and four numeric variables (`beer_servings`, `spirits_servints`, `wine_servings` and `total_litres_of_pure_alcohol`) for which we can also see some summary statistics showing that the data is right-skewed. There are no missing values as can be seen from the `n_missing` variable that is 0 for all five variables contained in the dataset.

We use `ggplot` to graph the top 25 consuming countries for beer, wine and spirits respectively.

```{r beer_plot}
alcohol_direct %>% 
  slice_max(order_by = beer_servings,
            n = 25) %>%    #pick only the top 25 countries with the most beer_servings
  ggplot(aes(x = beer_servings,
             y = fct_reorder(country, beer_servings))) + #order the country with beer_servings
  geom_col(fill = "gold",
           color = "grey") +
  labs(title="Top 25 beer consuming countries",
       x = "Number of Beer Servings",
       y = "Country") +
  coord_cartesian(xlim = c(100,NA)) +
  NULL
```

```{r wine_plot}
alcohol_direct %>% 
  slice_max(order_by = wine_servings,
            n = 25) %>%
  ggplot(aes(x = wine_servings,
             y = fct_reorder(country, wine_servings))) +
  geom_col(fill = "deeppink4",    #choose the most wine-like color in the list of color table
           color = "grey") +
  labs(title = "Top 25 wine consuming countries",
       x = "Number of Wine Servings",
       y = "Country") +
  coord_cartesian(xlim = c(100,NA)) +
  NULL
```

```{r spirit_plot, fig.height=5}
alcohol_direct %>% 
  slice_max(order_by = spirit_servings,
            n = 25) %>%
  ggplot(aes(x = spirit_servings,
             y = fct_reorder(country,
                           spirit_servings))) +
  geom_col(fill = "cornsilk3", color = "grey") +
  labs(title = "Top 25 spirits consuming countries",
       x = "Number of Spirit Servings",
       y = "Country") +
  coord_cartesian(xlim = c(100,NA)) +
  NULL
```

> We can infer from the above graphs...

On a high-level overview we observe different countries being in the top spots for each type of alcohol.

- Beginning with **beer** consumption, the top 5 spots are dominated by central and eastern European countries with a few "surprises". Namibia apparently has a long history of beer production. According to CNN, the first Namibian brewery opened in 1900, with every ethnic group in Africa having its own methods to create the famous beverage. Nowadays local beer is a tourist attraction and a large source of revenues for both Namibia and Ghana, explaining their placement in the list. As for the rest of the countries comprising the top 5, it is known that beer is very inexpensive there, with Czech Republic offering beer at a lower price than water in some pubs and restaurants.

- Moving to **wine**, the top spot is with France (arguably) highly anticipated. Bordeaux, a rural city in France has got some of the world's finest wineries, with its wine being beloved both locally and internationally. Similar reasoning applies to Portugal. Douro Port is the country's most famous wine, with many casual drinkers switching to premium wines, according to wininteligence.com. What is definitely worthy of commentary is Andorra's placement on the list, because of its small population ranking it amongst the six European countries with the least residents. Again, as Andorra is a famous tourist destination because of its ski resorts, the high wine consumption is mostly attributed to tourists.

- Finally, regarding **spirits** we have mixed signals about the top 5. Although we would most definitely expect eastern countries such as Russia, the motherland of Vodka to be high on the list, Grenada seems to be number one, with another Caribbean country, St. Lucia, following on fifth. According to jamaicaobserver.com, both countries seem to have problems with illegal consumption since 2014, when the WHO declared Grenada as the country with the highest alcohol per capita consumption in the Caribbean.
